---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
<!-- badges: end -->

```{r, echo=FALSE, results="hide", warning=FALSE, message=FALSE}
#library(pte)
devtools::load_all("~/Dropbox/pte")
devtools::load_all("~/Dropbox/ife")
load("~/Dropbox/ife/data/job_displacement_data.rda")
library(ggplot2)
library(dplyr)
```

# Interactive Fixed Effects (ife) Package


The `ife` package contains code to estimate treatment effects in a setup where a researcher has access to panel data (or, hopefully in the near future, repeated cross sections data) and where untreated potential outcomes are generated by an interactive fixed effects model.  

The package is not currently available on CRAN, but it can be the development version of the package can be installed from github by
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("bcallaway11/ife")
```

## Example

Next, we provide a brief example using the application from Callaway and Karami (2021).


```{r}
res <- ife(yname="earn",
           gname="first.displaced",
           tname="year",
           idname="id",
           data=job_displacement_data,
           nife=2,
           xformla=~1,
           zformla=~EDUC + race + gender + afqt,
           ret_ife_regs=TRUE,
           anticipation=1,
           alp=0.1,
           biters=1000)

summary(res)
ggpte(res)
```
